Lossy compression of DNA sequencing quality data

### 2015-05-04 manuscript/q-compression.tex
Added spline regression.

>>>>

Profiles can be obtained from techniques other than $k$-means clustering.
%While we focus on profiles obtained from $k$-means clustering, other profiling techniques can be used in practice.
We can store the profiles of polynomial functions to increase the compressibility of polynomial regression modeling.
%For example, in order to increase the compressibility of polynomial regression modeling, we can store the profiles of polynomial functions.
In other words, we can use a spline (a function that is piecewise-defined by polynomial functions) to represent a given quality sequence.
Exploring other potential applications of profile-based compression is outside the scope of this work.
